### 2023-04-06 resilience.tex
up

\begin{example}
% Si on prends un Z-vass avec même seulement un compteur, Safe les entiers positifs, Bad le reste, avec juste une transition qui fait +1, alors on a la résilience (on reviens toujours dans les positifs) mais pas la bounded resilience.
Let us consider now a $\mathds{Z}$-VASS with only one state, one counter, and one transition that adds $+1$ to the counter, with $\Safe = \uparrow q(0)$, $\Bad = \downarrow q(-1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience
(for every bound $b$ there is an element of $\Bad$ e.g. $q(-b-1)$ which necessitate at least $b+1$ steps before it can reach $\Safe$). 
\end{example}

>>>>

\begin{example}
% Si on prends un Z-vass avec même seulement un compteur, Safe les entiers positifs, Bad le reste, avec juste une transition qui fait +1, alors on a la résilience (on reviens toujours dans les positifs) mais pas la bounded resilience.
Let us consider now a $\mathds{Z}$-VASS with only one state $q$, one counter, and one transition that adds $+1$ to the counter, with $\Safe = \uparrow q(0)$, $\Bad = \downarrow q(-1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience
(for every bound $b$ there is an element of $\Bad$ e.g. $q(-b-1)$ which necessitate at least $b+1$ steps before it can reach $\Safe$). 
\end{example}
